\subsection{Suite and evaluation grid}
This paper evaluates model-assisted tabular ML work over a four-competition suite and three time budgets (240s, 600s, 1200s). The 1200s configuration uses an XGBoost-focused instruction set.

Each time budget uses a fixed instruction set, so the 240s/600s/1200s settings differ in both available time and the instructions given to the agent.

Reporting is restricted to models that reached complete five-run coverage across all 12 task$\times$budget settings (4 competitions $\times$ 3 time budgets). Under that rule, 10 models are included in the main tables.

\subsection{Prompt strategy and aggregation rule}
A fixed instruction template is used for all runs in this paper.

For each \texttt{(competition, model, budget)} setting, the reported value is the median of the earliest 5 successful runs ordered by \texttt{created\_at}.

\subsection{Evaluation logging and reproducibility}
The evidence in this paper is derived from logged run outcomes (status, score, runtime, and run configuration). I focus only on models with complete coverage: five successful runs for every task$\times$budget setting included in the benchmark.

\subsection{Agent harness (Kilo Code)}
Each run is executed in a clean, per-run workspace managed by the Kilo Code harness. The harness enforces the time budget, validates the submission format, and scores submissions on hidden holdout labels (not accessible to the agent).

Appendix~\ref{sec:appendix-harness} describes what Kilo Code is and why this paper standardizes on it.

\subsection{Contamination controls}
This paper uses two controls to reduce contamination risk from external information. First, internet access is disabled during benchmark runs. Second, evaluated models are selected so that their pretraining knowledge cutoff predates the start date of each tested Kaggle competition. In this suite, the earliest competition release is in late October 2025, and all listed cutoff dates in Appendix~\ref{sec:appendix-models} precede that date.

\subsection{Metrics and normalization}
Each competition has a task-defined metric. This paper reports \texttt{score\_raw} in the task's native direction (for example, AUC where higher is better, and RMSE where lower is better).

Raw metric values are not comparable across competitions because they have different scales and different directions. To build aggregate leaderboards and scaling plots, this paper uses a within-setting min-max normalization:
\begin{itemize}
  \item For each \texttt{(competition, budget)} setting, compute each model's five-run median \texttt{score\_raw}.
  \item Convert to a common ``higher is better'' value: \texttt{value\_hib = score\_raw} for higher-is-better metrics, and \texttt{value\_hib = -score\_raw} for lower-is-better metrics.
  \item Min-max normalize within that setting so the best model gets 1.0 and the worst gets 0.0:
    \[
      \mathrm{score} = \frac{\mathrm{value\_hib} - \min(\mathrm{value\_hib})}{\max(\mathrm{value\_hib}) - \min(\mathrm{value\_hib})}.
    \]
\end{itemize}

Appendix~\ref{sec:appendix-method} defines the normalization and the primary aggregation precisely.

\subsection{Time budgets}
This paper evaluates three wall-clock time budgets per competition: 240 seconds, 600 seconds, and 1200 seconds. A time budget represents the total time available to the agent to read the task, train, iterate, and produce a final submission file.

Implementation details (what ``240s'' means in practice):
\begin{itemize}
  \item The time budget applies to the agent interaction stage, enforced as a hard timeout by the Kilo Code harness.
  \item Runtime is measured from run start to the end of the agent stage (or timeout). Validation and private-holdout scoring occur after this stage and do not count against the time budget.
  \item If the harness observes that the agent exceeded the time budget (with a small grace window for timing granularity), the run is marked as a timeout even if a submission file exists.
\end{itemize}

Time budgets are included because ``fast baseline'' and ``iterative improvement'' are different capabilities. A strict budget makes these trade-offs visible under a repeatable protocol.
